% ***********************************************************************
%
% Acknowledgement
% 
% ***********************************************************************

\chpos{14mm}{10mm}
\chapter*{Acknowledgement}
\markboth{Acknowledgement}{Acknowledgement}
\addcontentsline{toc}{chapter}{Acknowledgement}

The beauty of reaching a goal, besides exciting discoveries, is likewise based on the fact that a journey towards the goal often involves overcoming various hurdles. Here, I would like to acknowledge people that had helped along that journey and made reaching the goal possible.

I am very grateful to my co-promotor Erik Meijering and promotor Prof. Wiro Niessen for giving me the opportunity to do research job and for having enough patience and trust. The experience gained at Biomedical Imaging Group Rotterdam allowed discovering the world better and shaped up my views on work and life. I equally owe my supervisor a debt of gratitude for all the dedication in crafting the publications and beautiful writing suggestions that brought the work to a higher standard.

The Netherlands Organization for Scientific Research (NWO) deserves appreciation for funding the project together with all the reviewers for their constructive feedback.

I owe special gratitude to the colleagues and collaborators Ihor, Gadea, Carlos and Niels that contributed building this work up. Many thanks to Petra and Desiree for the administrative support and to all past and present members of Medical Informatics and Radiology Department.

From the bottom of my heart, I wish to thank my dear friends, one very special cousin, my parents Milija and Vera, my sister Danica and my girlfriend Letizia for all the genuine kindness and support one could wish for.  

\bigskip
\begin{flushright}
  \begin{tabular}{@{}l@{}}
    Miroslav Radojevi\'{c}\\
    Rotterdam, October 2018
  \end{tabular}
\end{flushright}
% ************************************************************************
