% ************************************************************************
%
% Curriculum Vitae
%
% ************************************************************************

\noquote
\orgchpos
\chapter*{Curriculum Vitae}
\markboth{Curriculum Vitae}{Curriculum Vitae}
\addcontentsline{toc}{chapter}{Curriculum Vitae}

% ************************************************************************
\noindent
Miroslav Radojevi\'{c} was born in U\v{z}ice, Serbia, on January 7, 1984. He received a B.Sc. degree in Electrical Engineering from the University of Belgrade - School of Electrical Engineering, Serbia, in 2008.
\bigskip

\noindent
From 2008 to 2009, he was a Development Engineer with ABS Electro. During that period he developed protection algorithms for digital protective relays.
\bigskip

\noindent 
In 2009 he was awarded Erasmus Mundus scholarship by the European Commission and from 2009 to 2011 took part in the international master programme in Computer Vision and Robotics (ViBot) offered by a consortium of the Heriot-Watt University (United Kingdom), Universit\`{e} de Bourgogne (France) and Universitat de Girona (Spain). In 2011 he received a M.Sc. degree graduating on the underwater robotics project ``Underwater Vehicle Localization using Extended Kalman Filter''. During that period he participated in 2011 edition of the SAUC-E Student AUV Challenge Europe.  
\bigskip

\noindent
From Dec. 2011 to Feb. 2016 he was a Ph.D. student at the Departments of Medical Informatics and Radiology of the Erasmus University Rotterdam, the Netherlands. His research topic was automated reconstruction of neuron cells in microscopy images. The results are described in this thesis.
\bigskip

\noindent
Since 2017, he has been a software engineer with Becton, Dickinson and Company (BD), working at the research and development department within BD Life Sciences.